---
title: "C636 analysis"
author: "Clay Ford"
date: "Friday, April 24, 2015"
output: pdf_document
---

Some preliminary analyses per our discussion on 24-April-2015. **Note that the source file contains missing values in cells Q1188 AND U1534**.


```{r, echo=FALSE}
load("c636.RData")

```

Below are points of interest. That is, values with z-score exceeding of 2.99 in either direction. The missing values (indicated with NA) are due to missing values in the source file.


```{r}
zscoresL[abs(zscoresL$value)>2.99,]
```

Here are some strip charts. Lab plates 6, 18, 21, 38 and 59 all have major outlying values.

```{r, echo=FALSE}
# create a stripchart for a given lab plate
# num = the lab plate number
labPlot <- function(num){
  op <- par(mai=c(0.5,2,0.5,0.5))
  stripchart(value ~ variable, data=zscoresL, subset= LAB.plate==num, pch=1, jitter = T, las=1,
               main=paste("Lab Plate",num))
  abline(h=1:22,lty=3)  
  on.exit(op)
}

```

```{r}
for(i in levels(zscoresL$LAB.plate)){
  labPlot(num=i)
}

```



